%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Aidmics Biotechnology} % Organization
    {Aug. 2016 - Present} % Date(s
    {Taipei, Taiwan} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain product website and optimize web page delivery performance with node.js and postgreSQL.}
        \item {Integrate user-tracking with Facebook Business and Google Analytics and payment with Paypal API.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Intern} % Job title
    {Security Team, China Development Lab, IBM Taiwan} % Organization
    {Jul. 2015 - Jan. 2016} % Date(s)
    {Taipei, Taiwan} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed proof of concept for intrusion protection system cloud service with node.js and iptables on self-hosted Cloud Foundry instance and multi-tenant Openstack environment.}
        \item {Demonstrate possibility and performance of packet inspection with Netfilter/NFQUEUE inside Docker containers by implementing daemons written in C.}
        \item {Inventor of US patent regarding intrusion protection for connections with TLS resumption.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Fullstack Web Developer Intern} % Job title
    {Bonio Inc.} % Organization
    {Jul. 2014 - Sep. 2014} % Date(s)
    {Taipei, Taiwan} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed game prototype for project management training using Ruby on Rails.}
        \item {Deployed Scrum in project team as the agile software development framework.}
      \end{cvitems} 
    }
\end{cventries}
