\cvsection{Extra-Curricular Activities}
  \begin{cventries}
    \cventry
      {Director of Community \& Club Leader}
      {HackNTU}
      {Oct. 2014 - Jul. 2015}
      {}
      {
        \begin{cvitems}
          \item {Organized a total of 5 workshops and meetups with a target audience of non-tech background students, introducing them to topics such as web design, hardware hacking and data science.}
          \item {Managed and coordinated 4 semester-wide courses held by the club collaborating with instructors from IT industry covering subjects such as IoT and mobile apps. }
        \end{cvitems}
      }
    \cventry
      {Chief Information Officer}
      {NTUEE Student Association}
      {Sep. 2014 - Aug. 2015}
      {}
      {
        \begin{cvitems}
          \item {Developed and maintained textbook purchasing system that was used by students from 4 departments. The system was developed with Ruby on Rails.}
          \item {Establish and managed Linux server used by student association.}
        \end{cvitems}
      }
    \cventry
      {Director of Marketing}
      {NTU Securities Research Society}
      {Nov. 2013 - Feb. 2015}
      {}
      {
        \begin{cvitems} % Description(s) of experience/contributions/knowledge
          \item {Improved exposure and attendance of events by managing social media with advertising campaigns.}
          \item {Organized and promoted camps for 50 participants from general public to gain knowledge on securities and financial markets.}
        \end{cvitems}
      }
  \end{cventries}
