\cvsection{Research and Patents}
  \begin{cventries}
    \cventry
      {Undergraduate Research}
      {Fast Crypto Lab, NTUEE}
      {Fall 2015 - Spring 2016}
      {}
      {
        \begin{cvitems}
          \item {Reproduced attack in paper\footnotemark[1] on MIFARE classic cards based on design flaws in Crypto-1 with C++.}
          \item {Used multiple methods to reduce complexity from 2\textsuperscript{48} to 2\textsuperscript{33.7}. }
        \end{cvitems}
      }
    \cventry
      {Patent Inventor}
      {Security Team, China Development Lab, IBM Taiwan}
      {Jul. 2015 - Jan. 2016}
      {}
      {
        \begin{cvitems}
          \item {US Patent: Seamless Abort and Reinstatement of TLS Session (IBM Docket No. TW920160011US1)}
          \item {Co-invented method allowing passive inspectors to transparently handle existing TLS connections with resumption.}
        \end{cvitems}
      }
    \cventry
      {Undergraduate Research}
      {Wireless and Mobile Network Lab, NTUEE}
      {Spring 2015}
      {}
      {
        \begin{cvitems}
          \item {Analyzed wireless networking models with game theory and other optimization methods(e.g. Dual Analysis, Lyapunov Stability).}
          \item {Formulated user association model of LTE/LTE-U spectrum with multiple UEs}
        \end{cvitems}
      }
  \end{cventries}
  \footnotetext[1]{Carlo Meijer and Roel Verdult. “Ciphertext-only Cryptanalysis on Hardened Mifare Classic Cards”. 22nd ACM SIGSAC Conference on Computer and Communications Security. CCS ’15}